PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-06-16 manuscript_00.Rmd
updates

```{r}
spec_diff <- diff_tab_big %>% 
  filter(Symbol %in% diff_tab$Symbol) %>% # only retain diff genes across "All"
  group_by(Symbol, Organism, Base) %>% 
  summarise(Count = n()) %>% 
  summarise(Count = n())

spec_diff_go <- spec_diff %>% 
  filter(Count <= 3) %>% 
  mutate(go = paste(Symbol, '___', Organism, sep = '')) %>% 
  pull(go)

diff_tab_big %>% 
  filter(Symbol %in% diff_tab$Symbol) %>% # only retain diff genes across "All"
  group_by(Symbol, Organism, Base) %>% 
  summarise(Count = n(),
            baseMean = mean(baseMean),
            log2FoldChange = mean(log2FoldChange),
            padj = mean(padj)) %>% 
  filter(Count > 1) %>% 
  left_join(spec_diff, by = c("Symbol", "Organism")) %>% 
  mutate(Ratio = `Count.x` / `Count.y`) %>% 
  select(-`Count.x`,-`Count.y`) %>% 
  #mutate(go = paste(Symbol, '___', Organism, sep = '')) %>% 
  #filter(go %in% (spec_diff_go))  %>% 
  #select(-go) %>% 
  ungroup() %>% 
  group_by(Organism, Base) %>% 
  slice_max(n = 10, order_by = log2FoldChange)

@@

### heatmap human
```{r, fig.width=5, fig.height=20}
diff_ratios <- diff_tab_big %>% 
    filter(Against != 'All') %>% 
    group_by(Symbol, ID, Organism, Base) %>% 
    summarise(Count = n()) %>% 
    filter(Count > 1) %>% 
    left_join(spec_diff, by = c("Symbol", "Organism")) %>% 
    mutate(Ratio = `Count.x` / `Count.y`) %>% 
    select(Symbol:Base, Ratio)

gene_sets <- diff_tab %>% 
  left_join(diff_ratios, by = c('Symbol', 'ID','Base','Organism')) %>% 
  filter(Ratio > 0.2) %>% group_by(Base, Organism) %>% 
  slice_max(n=5, order_by = log2FoldChange)

@@

x <- scEiaD_2020_v01 %>% 
  tbl("diff_testing") %>% 
  filter(Gene %in% g, Base %in% ct) %>% 
  collect() %>% 
  filter(Group == 'CellType (Predict)', 
         Organism == org, Against == 'All') %>% 
  select(Gene, log2FoldChange, Base) %>% 
  pivot_wider(values_from=log2FoldChange, names_from = Base) 
celltype <- colnames(x[,-1])
x <- x %>% data.frame()
row.names(x) <- x$Gene
x <- x[,-1]
Heatmap(x, column_labels = celltype)
```

@@

x <- scEiaD_2020_v01 %>% 
  tbl("diff_testing") %>% 
  filter(Gene %in% g, Base %in% ct) %>% 
  collect() %>% 
  filter(Group == 'CellType (Predict)', 
         Organism == org, Against == 'All') %>% 
  select(Gene, log2FoldChange, Base) %>% 
  pivot_wider(values_from=log2FoldChange, names_from = Base) 
celltype <- colnames(x[,-1])
x <- x %>% data.frame()
row.names(x) <- x$Gene
x <- x[,-1]
Heatmap(x, column_labels = celltype)
```

>>>>

```{r}
scEiaD_2020_v01 %>% 
    tbl("diff_testing") %>% 
    filter(Base == 'Cone') %>%  
    filter(Group == 'CellType (Predict)', 
           Against == 'All') %>% 
  group_by(Gene) %>% 
  summarise(Count = n(), log2FoldChange = mean(log2FoldChange), padj_count = sum(padj < 1e-4), padj = mean(padj)) %>% 
  filter(!is.na(log2FoldChange), padj_count > 1) %>%  
  arrange(-log2FoldChange)

@@

### heatmap human
```{r, fig.width=6, fig.height=17}
# diff_ratios <- diff_tab_big %>% 
#     filter(Against != 'All') %>% 
#     group_by(Symbol, ID, Organism, Base) %>% 
#     summarise(Count = n()) %>% 
#     filter(Count > 1) %>% 
#     left_join(spec_diff, by = c("Symbol", "Organism")) %>% 
#     mutate(Ratio = `Count.x` / `Count.y`) %>% 
#     select(Symbol:Base, Ratio)

gene_sets <- diff_tab %>% 
  #left_join(diff_ratios, by = c('Symbol', 'ID','Base','Organism')) %>% 
  #filter(Ratio > 0.2) %>% 
  group_by(Base, Organism) %>% 
  slice_max(n=5, order_by = log2FoldChange)

@@

x <- scEiaD_2020_v01 %>% 
  tbl("diff_testing") %>% 
  filter(Gene %in% g) %>% 
  collect() %>% 
  filter(Base %in% ct,
         Group == 'CellType (Predict)', 
         Organism == org, Against == 'All') %>% 
  select(Gene, log2FoldChange, Base) %>% 
  pivot_wider(values_from=log2FoldChange, names_from = Base) 
celltype <- colnames(x[,-1])
x <- x %>% data.frame()
row.names(x) <- x$Gene
x <- x[,-1]
Heatmap(x, column_labels = celltype)
```

@@

x <- scEiaD_2020_v01 %>% 
  tbl("diff_testing") %>% 
  filter(Gene %in% g) %>% 
  collect() %>% 
  filter(Group == 'CellType (Predict)', 
         Organism == org, Against == 'All', Base %in% ct) %>% 
  select(Gene, log2FoldChange, Base) %>% 
  pivot_wider(values_from=log2FoldChange, names_from = Base) 
celltype <- colnames(x[,-1])
x <- x %>% data.frame()
row.names(x) <- x$Gene
x <- x[,-1]
Heatmap(x, column_labels = celltype)
```
